---
title: "SummaryStats"
author: "Adam Imran"
date: "3/12/2020"
output: html_document
---
## initial data loading
```{r}
Traffic_Weather = read.csv("Traffic_Violations_Clean.csv")
# Removal of the first column
Traffic_Weather = Traffic_Weather[,-1]
```

## Dates
```{r}
# Import lubridate package
library(lubridate)
# Convert the type to date time
Traffic_Weather$Date.time = ymd_hms(Traffic_Weather$Date.time)
# Extract the minimum
min(Traffic_Weather$Date.time)
#Extract the maximum
max(Traffic_Weather$Date.time)
```

## Subagency
```{r}
summary(Traffic_Weather$SubAgency)
## Subagency with the most accidents - Wheaton
sort(summary(Traffic_Weather$SubAgency))[length(summary(Traffic_Weather$SubAgency))]
## Subagency with the most personal injuries - Wheaton
sort(summary(Traffic_Weather$SubAgency[Traffic_Weather$Personal.Injury == "Yes"]))[7]
```
Subagency with the most pullovers - Wheaton

## Top five crimes in the dataset
```{r}
sort(summary(Traffic_Weather$Description),decreasing = T)[2:6]
```

## Top 5 locations
```{r}
sort(summary(Traffic_Weather$Location), decreasing = T)[1:5]
```

## Deep dive What made these locations so ripe for being pulled over
```{r}
## Not stopping at a red light
sort(summary(Traffic_Weather$Description[Traffic_Weather$Location =="MONTGOMERY VILLAGE AVE @ RUSSELL AVE"]), decreasing = T)[1:3]
## Speeding
sort(summary(Traffic_Weather$Description[Traffic_Weather$Location =="RIVER RD AND ROYAL DOMINION"]), decreasing = T)[1:3]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Location =="RIVER RD @ ROYAL DOMINION DR"]), decreasing = T)[1:3]
```

MONTGOMERY VILLAGE AVE @ RUSSELL AVE intersection is big for not following traffic signals

RIVER RD AND ROYAL DOMINION is big for speeding

## Summary stats for temperature
```{r}
summary(Traffic_Weather$Temperature)
```

## Summary stats of Windchill
```{r}
summary(Traffic_Weather$Wind.Chill)
```

## Summary stats of Heat.Index
```{r}
summary(Traffic_Weather$Heat.Index)
```

## Summary stats of Precipitation
```{r}
summary(Traffic_Weather$Precipitation)
```

## Summary stats of Snow
```{r}
summary(Traffic_Weather$Snow.Depth)
```

## Summary stats of Wind
```{r}
summary(Traffic_Weather$Wind.Speed)
```

## Summary stats of Cloud Cover
```{r}
summary(Traffic_Weather$Cloud.Cover)
```

## Summary stats of Conditions
```{r}
summary(Traffic_Weather$Conditions)[1:3]
```

## Summary stats of Accidents
```{r}
summary(Traffic_Weather$Accident)
## Top location for accidents is HEWITT AVE & RIPPLING BROOK DR Bel Pre Elementary School
sort(summary(Traffic_Weather$Location[Traffic_Weather$Accident == "Yes"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Accident == "Yes"]), decreasing = T)[1:5]
```

## Summary stats of Personal Injury
```{r}
summary(Traffic_Weather$Personal.Injury)
sort(summary(Traffic_Weather$Location[Traffic_Weather$Personal.Injury == "Yes"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Personal.Injury == "Yes"]), decreasing = T)[1:5]
```

## Summary stats for Property damage
```{r}
summary(Traffic_Weather$Property.Damage)
sort(summary(Traffic_Weather$Location[Traffic_Weather$Property.Damage == "Yes"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Property.Damage == "Yes"]), decreasing = T)[1:5]
```


## Summary stats for fatal
```{r}
summary(Traffic_Weather$Fatal)
sort(summary(Traffic_Weather$Location[Traffic_Weather$Fatal == "Yes"]), decreasing = T)[1:5]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Fatal == "Yes"]), decreasing = T)[1:5]
```

## Summary stats of Alcohol
```{r}
summary(Traffic_Weather$Alcohol)
sort(summary(Traffic_Weather$Location[Traffic_Weather$Alcohol == "Yes"]), decreasing = T)[1:5]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Alcohol == "Yes"]), decreasing = T)[1:5]
```

## Top reasons searches were conducted
## Where they were conducted
## What was the cause
```{r}
summary(Traffic_Weather$Search.Conducted)
sort(summary(Traffic_Weather$Location[Traffic_Weather$Search.Conducted == "Yes"]), decreasing = T)[1:5]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Search.Conducted == "Yes"]), decreasing = T)[1:5]
```

## Search disposition
```{r}
sort(summary(Traffic_Weather$Search.Disposition), decreasing = T)
```

## What kind of search was done
```{r}
sort(summary(Traffic_Weather$Search.Type), decreasing = T)
```

## State
```{r}
sort(summary(Traffic_Weather$State), decreasing = T)
```

## Reason someone was searched
```{r}
sort(summary(Traffic_Weather$Search.Reason),decreasing = T)[1:5]
```

## What kind of vehicle was stopped and what color
```{r}
sort(summary(Traffic_Weather$Color), decreasing = T)[1:5]
sort(summary(Traffic_Weather$VehicleType), decreasing = T)[1:5]
```


## Racial Breakdown - Black
## Where it occured
## What was the search used
## Why were they searched
```{r}
summary(Traffic_Weather$Race)
sort(summary(Traffic_Weather$Location[Traffic_Weather$Race == "BLACK"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Race == "BLACK"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Search.Disposition[Traffic_Weather$Race == "BLACK"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Search.Reason[Traffic_Weather$Race == "BLACK"]), decreasing = T)[2:6]
```

## Racial Breakdown - White
## Where it occured
## What was the search used
## Why were they searched
```{r}
sort(summary(Traffic_Weather$Location[Traffic_Weather$Race == "WHITE"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Race == "WHITE"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Search.Disposition[Traffic_Weather$Race == "WHITE"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Search.Reason[Traffic_Weather$Race == "WHITE"]), decreasing = T)[2:6]
```

## Racial Breakdown - Hispanic
## Where it occured
## What was the search used
## Why were they searched
```{r}
sort(summary(Traffic_Weather$Location[Traffic_Weather$Race == "HISPANIC"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Race == "HISPANIC"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Search.Disposition[Traffic_Weather$Race == "HISPANIC"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Search.Reason[Traffic_Weather$Race == "HISPANIC"]), decreasing = T)[2:6]
```

## Racial Breakdown - Asian
## Where it occured
## What was the search used
## Why were they searched
```{r}
sort(summary(Traffic_Weather$Location[Traffic_Weather$Race == "ASIAN"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Description[Traffic_Weather$Race == "ASIAN"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Search.Disposition[Traffic_Weather$Race == "ASIAN"]), decreasing = T)[2:6]
sort(summary(Traffic_Weather$Search.Reason[Traffic_Weather$Race == "ASIAN"]), decreasing = T)[2:6]
```

## Gender
## What kinds of things did females get pulled over for?
```{r}
summary(Traffic_Weather$Gender)
sort(summary(Traffic_Weather$Description[Traffic_Weather$Gender == "F"]), decreasing = T)[2:6]
```

## Where do these drivers come from?
```{r}
sort(summary(Traffic_Weather$Driver.City), decreasing = T)
```

## How many got arrested and what caused their arrest?
```{r}
summary(Traffic_Weather$Arrest)
sort(summary(Traffic_Weather$Description[Traffic_Weather$Arrest == T]), decreasing = T)[1:5]
```

## Reaason for arrest
```{r}
summary(Traffic_Weather$Arrest.Reason)
sort(summary(Traffic_Weather$Description[Traffic_Weather$Arrest.Reason == "Stop"]), decreasing = T)[2:6]
```

